A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-02 paper/paper.tex
Missing D' <- clone(D) in algorithm
Fix fonts of T and P (Review 2)
Hint on how to verify the proposition (Review 2)
Muck around with G^[c, l] notation (Review 2)

A \emph{path} in a graph is a sequence of distinct vertices, such that each successive pair of
vertices are adjacent; we also allow a path from a vertex to itself, in which case the first and
last vertices in the sequence are the same (and there is a \emph{cycle}). The \emph{distance}
between two vertices is the length of a shortest path between them. We write $G^d$ for the graph
with vertex set $\operatorname{V}(G)$, and edges between $v$ and $w$ if the distance between $v$ and
$w$ in $G$ is at most $d$.  We introduce the notation $G^{\left[n, m\right]}$ for the graph with
vertex set $\operatorname{V}(G)$, and edges between vertices $v$ and $w$ (not necessarily distinct)
precisely if there are at least $m$ paths of length exactly $n$ between $v$ and $w$ in $G$. The
following proposition may easily be verified:

\begin{proposition}\label{proposition:supplemental}
    Let $i : P \hookrightarrow T$ be a subgraph isomorphism. Then $i$ is also
    \begin{enumerate}[itemindent=1em,topsep=0pt,itemsep=0.2pt]
        \item a subgraph isomorphism $i^d : P^d \hookrightarrow T^d$ for any $d \ge 1$, and
        \item a subgraph isomorphism $i^{\left[n, m\right]} : P^{\left[n, m\right]} \hookrightarrow
            T^{\left[n, m\right]}$ for any $n, m \ge 1$.
    \end{enumerate}
\end{proposition}

@@

Our choice of supplemental graphs is somewhat arbitrary. We observe that distances of greater than 3
rarely give additional filtering power, and constructing $G^{\left[4,n\right]}$ is computationally
very expensive (for unbounded $m$, the construction is \NP-hard). Checking $n > 3$ is also rarely
beneficial. Our choices work reasonably well in general on the wide range of benchmark instances we
consider, but can be expensive for trivial instances---thus there is potential room to improve the
algorithm by better selection on an instance by instance basis \cite{Malitsky:2014}.

\begin{algorithm}[h]
\DontPrintSemicolon
\nl $\FuncSty{createSupplementalGraphs}$ (Graph $P$, Graph $T$) $\rightarrow$ GraphPairs \;
\nl \Begin{
    \nl $\begin{aligned}\KwSty{return}~\Big\{
            &(\mathcal{P},\ \mathcal{T}),
            &&(\mathcal{P}^{\left[2,1\right]},\ \mathcal{T}^{\left[2,1\right]}),
            &&(\mathcal{P}^{\left[2,2\right]},\ \mathcal{T}^{\left[2,2\right]}),
            &&(\mathcal{P}^{\left[2,3\right]},\ \mathcal{T}^{\left[2,3\right]}), \\
            &&&(\mathcal{P}^{\left[3,1\right]},\ \mathcal{T}^{\left[3,1\right]}),
            &&(\mathcal{P}^{\left[3,2\right]},\ \mathcal{T}^{\left[3,2\right]}),
            &&(\mathcal{P}^{\left[3,3\right]},\ \mathcal{T}^{\left[3,3\right]})
    \Big\}\end{aligned}$ \;
}
\caption{Supplemental graphs for \cref{algorithm:sip}}
\label{algorithm:supplemental}
\end{algorithm}

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\SetKwSwitch{Switch}{Case}{Other}{case}{of}{}{otherwise}{endcase}{endsw}
\nl $\FuncSty{search}$ (GraphPairs $G$, Domains $D$) $\rightarrow$ Fail $F$ \KwSty{or} Success \;
\nl \Begin{
    \nl \lIf {$D = \emptyset$}{$\KwSty{return}~\textnormal{Success}$\label{line:success}}
    \nl $D_v \gets \textnormal{a domain in $D$ with minimum size, tiebreaking on static degree in}~\mathcal{P}$ \label{line:branch} \;
    \nl $F \gets \{ v \}$ \label{line:fcurrent} \;
    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
        \nl \Switch{$\FuncSty{assign}(G, D', v, v')$\label{line:assign}}{
            \nl \lCase{\textnormal{Fail $F'$~\KwSty{then}}}{$F \gets F \cup F'$\label{line:fassign}}
            \nl \Case{\textnormal{Success~\KwSty{then}}}{
                \nl \Switch{$\FuncSty{search}(G, D' - D_v)$\label{line:recursesearch}}{
                    \nl \lCase{\textnormal{Success~\KwSty{then}}}{$\KwSty{return}~\textnormal{Success}$}
                    \nl \Case{\textnormal{Fail $F'$~\KwSty{then}}\label{line:searchfailed}}{
                        \nl \If{$\nexists\,w \in F'~\KwSty{such that}~D_w \ne D'_w$}{
                        \nl $\KwSty{return}~\textnormal{Fail}~F'$\label{line:backjump}}
                        \nl $F \gets F \cup F'$ \label{line:fsub} \;
                    }
                }
            }
        }
    }
    \nl $\KwSty{return}~\textnormal{Fail}~F$ \;
}
\caption{Recursive search for \cref{algorithm:sip}}
\label{algorithm:search}
\end{algorithm}

>>>>

A \emph{path} in a graph is a sequence of distinct vertices, such that each successive pair of
vertices are adjacent; we also allow a path from a vertex to itself, in which case the first and
last vertices in the sequence are the same (and there is a \emph{cycle}). The \emph{distance}
between two vertices is the length of a shortest path between them. We write $G^d$ for the graph
with vertex set $\operatorname{V}(G)$, and edges between $v$ and $w$ if the distance between $v$ and
$w$ in $G$ is at most $d$.  We introduce the notation $G^{\left[c, l\right]}$ for the graph with
vertex set $\operatorname{V}(G)$, and edges between vertices $v$ and $w$ (not necessarily distinct)
precisely if there are at least $c$ paths of length exactly $l$ between $v$ and $w$ in $G$. The
following proposition may easily be verified (by observing that injectivity means paths are
preserved):

\begin{proposition}\label{proposition:supplemental}
    Let $i : P \hookrightarrow T$ be a subgraph isomorphism. Then $i$ is also
    \begin{enumerate}[itemindent=1em,topsep=0pt,itemsep=0.2pt]
        \item a subgraph isomorphism $i^d : P^d \hookrightarrow T^d$ for any $d \ge 1$, and
        \item a subgraph isomorphism $i^{\left[c, l\right]} : P^{\left[c, l\right]} \hookrightarrow
            T^{\left[c, l\right]}$ for any $c, l \ge 1$.
    \end{enumerate}
\end{proposition}

@@

Our choice of supplemental graphs is somewhat arbitrary. We observe that distances of greater than 3
rarely give additional filtering power, and constructing $G^{\left[c, 4\right]}$ is computationally
very expensive (for unbounded $l$, the construction is \NP-hard). Checking $c > 3$ is also rarely
beneficial. Our choices work reasonably well in general on the wide range of benchmark instances we
consider, but can be expensive for trivial instances---thus there is potential room to improve the
algorithm by better selection on an instance by instance basis \cite{Malitsky:2014}.

\begin{algorithm}[h]
\DontPrintSemicolon
\nl $\FuncSty{createSupplementalGraphs}$ (Graph $\mathcal{P}$, Graph $\mathcal{T}$) $\rightarrow$ GraphPairs \;
\nl \Begin{
    \nl $\begin{aligned}\KwSty{return}~\Big\{
            &(\mathcal{P},\ \mathcal{T}),
            &&(\mathcal{P}^{\left[1,2\right]},\ \mathcal{T}^{\left[1,2\right]}),
            &&(\mathcal{P}^{\left[2,2\right]},\ \mathcal{T}^{\left[2,2\right]}),
            &&(\mathcal{P}^{\left[3,2\right]},\ \mathcal{T}^{\left[3,2\right]}), \\
            &&&(\mathcal{P}^{\left[1,3\right]},\ \mathcal{T}^{\left[1,3\right]}),
            &&(\mathcal{P}^{\left[2,3\right]},\ \mathcal{T}^{\left[2,3\right]}),
            &&(\mathcal{P}^{\left[3,3\right]},\ \mathcal{T}^{\left[3,3\right]})
    \Big\}\end{aligned}$ \;
}
\caption{Supplemental graphs for \cref{algorithm:sip}}
\label{algorithm:supplemental}
\end{algorithm}

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\SetKwSwitch{Switch}{Case}{Other}{case}{of}{}{otherwise}{endcase}{endsw}
\nl $\FuncSty{search}$ (GraphPairs $G$, Domains $D$) $\rightarrow$ Fail $F$ \KwSty{or} Success \;
\nl \Begin{
    \nl \lIf {$D = \emptyset$}{$\KwSty{return}~\textnormal{Success}$\label{line:success}}
    \nl $D_v \gets \textnormal{a domain in $D$ with minimum size, tiebreaking on static degree in}~\mathcal{P}$ \label{line:branch} \;
    \nl $F \gets \{ v \}$ \label{line:fcurrent} \;
    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
        \nl $D' \gets \FuncSty{clone}(D)$ \;
        \nl \Switch{$\FuncSty{assign}(G, D', v, v')$\label{line:assign}}{
            \nl \lCase{\textnormal{Fail $F'$~\KwSty{then}}}{$F \gets F \cup F'$\label{line:fassign}}
            \nl \Case{\textnormal{Success~\KwSty{then}}}{
                \nl \Switch{$\FuncSty{search}(G, D' - D_v)$\label{line:recursesearch}}{
                    \nl \lCase{\textnormal{Success~\KwSty{then}}}{$\KwSty{return}~\textnormal{Success}$}
                    \nl \Case{\textnormal{Fail $F'$~\KwSty{then}}\label{line:searchfailed}}{
                        \nl \If{$\nexists\,w \in F'~\KwSty{such that}~D_w \ne D'_w$}{
                        \nl $\KwSty{return}~\textnormal{Fail}~F'$\label{line:backjump}}
                        \nl $F \gets F \cup F'$ \label{line:fsub} \;
                    }
                }
            }
        }
    }
    \nl $\KwSty{return}~\textnormal{Fail}~F$ \;
}
\caption{Recursive search for \cref{algorithm:sip}}
\label{algorithm:search}
\end{algorithm}
